module2_eco_pol_factors

### 2022-02-17 moduletwoanalysis.Rmd
coding module one
chisq test on demographic variables and perceived risk

---
title: "module2_eco_pol_factors"
output:
  output: 
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    keep_md: true
    theme: paper
    df_print: paged
---

@@

```{r cars}
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
module2 <- data.frame(moduletwo)
module2 %>%
  filter(!row_number() %in% c(1,2))

@@

@@

```{r}
codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean)
```

>>>>

---
title: "module2_eco_pol_factors"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    keep_md: true
    theme: paper
    df_print: paged
---

@@

```{r}
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
module2 <- data.frame(moduletwo)
module2 %>%
  filter(!row_number() %in% c(1,2))

@@

codedmodule2

@@

```{r, eval=TRUE}

# summary statistics for risks from different energy sources

codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean)
```

```{r}

# summary statistics for benefits from different energy sources

codedmodule2 %>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate Ben from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Ben) %>%
  arrange(mean)

#round off to two decimal places
```

```{r}
#summary statistics for nuclear energy accept, reject and reluctantly accept scale
codedmodule2 %>%
  summarize_at(vars(N_accept,N_reject,N_reluctantlyaccept), list(~mean(., na.rm = TRUE),~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE),~n())) %>%
  add_rownames() %>%
  gather(acceptance, value, -rowname) %>%
  separate(acceptance, c("N_accept", "var") ,  extra = "merge", fill = "left") %>%
  separate(var, c("Acceptance", "summary")) %>%
  spread(summary, value) %>%
  select(-rowname, -N_accept)%>%
  arrange(mean)

```{r}

# chi square test for risk perception from nuclear energy and gender, race

# first combine gender and caste variables

chitest <- codedmodule2 %>%
  select(Risky_Nuclear,Risky_Hydro, Risky_Hydro, Risky_Solar,Urban_Rural, Gender, Caste) %>%
  na.omit() %>%
  filter(!Caste=="Rather not say/Don't know")%>%
  unite(gendercaste, Gender, Caste, sep = "_", remove = FALSE)

chitest

```{r}

chisq.test(chitest$Risky_Nuclear, chitest$Urban_Rural)
```

```{r}
